Using best practices for forecasting biodiversity changes in breeding birds

### 2017-07-20 manuscript/draft.Rmd

>>>>

We made long term forecasts from 2014-2050 using CMIP5 multi-model ensemble
dataset as the source for climatic variables. Precipitation and temperature from
37 downscaled model runs [@brekke2013, see Table S1] using the RCP6.0 scenario
were averaged together to create a single ensemble used to calculate the
bioclimatic variables for North America. For NDVI we used the per-site average
values from 2000-2013 as a simple forecast. For observer effects (see below) each
site was set to have zero observer bias.
